### 2013-09-25 0_frontmatter/abstract.tex
for work in isprint

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,
  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For inexperienced researchers (such as this author when he began this research),
  who attempt to process either SAR or POLSAR data using existing computation algorithms
  which most of the time expect an additive and homoskedastic input,
  this thesis proposes alternative and more familiar additive and homoskedastic models.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the statistical estimation framework for (POL)SAR.

>>>>

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,
  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For example, for inexperienced researchers (such as this author when he began this research),
  this thesis proposes additive and homoskedastic models for both SAR and POLSAR data,
  which are simpler and more familiar.
They are helpful by keeping these inexperienced researchers from falling into several common traps in (POL)SAR data processing.
%For inexperienced researchers (such as this author when he began this research),
%  who attempt to process either SAR or POLSAR data using existing computation algorithms
%  which most of the time expect an additive and homoskedastic input,
%  this thesis proposes alternative and more familiar additive and homoskedastic models.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the statistical estimation framework for (POL)SAR.
